NEED A BETTER TITLE: A co-moving pair of bright stars \\ with very different metallicities and abundances

### 2017-04-15 paper/ms.tex
new item placeholder
note on scattering

In this section, we describe the data relevant to our discussion of the origin of the system.
The co-moving pair was initially discovered in our recent search
for co-moving pairs using the proper motions from Gaia DR1.
We refer the readers to \citealt{2016arXiv161202440O} and briefly describe the method here.
For a given pair, we performed a hypothesis test between the two hypotheses that
the two stars share the same 3D velocity vector and that they have
two independent 3D velocity vectors.
In the catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
the pair that we present here was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above a relatively conservative cut of 6 that we adopted.
Additionally, we have checked that we do not find any possible additional co-moving companions
to this pair even when we lower the selection threshold to less conservative but still reasonable values.
The pair is in fact classified as a double star system independently
in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).

@@

@@

% binary-single and binary-binary exchange
Another scenario that two unrelated stars may end up in a wide binary system
is multi-body gravitational scattering.
We consider the exchange probabilities in binary-single and binary-binary interactions.
Given their low binding energy compared to incoming velocity of field stars,
this is low.

>>>>

In this section, we describe the data relevant to our discussion of the origin of the system.
The co-moving pair was initially discovered in our recent search
for co-moving pairs using the proper motions from Gaia DR1.
We refer the readers to \citealt{2016arXiv161202440O} and briefly describe the method here.
For a given pair, we performed a hypothesis test between the two hypotheses that
the two stars share the same 3D velocity vector and that they have
two independent 3D velocity vectors.
In the catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
the pair that we present here was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above a relatively conservative cut of 6 that we adopted.
Additionally, we have checked that we do not find any possible additional co-moving companions
to this pair even when we lower the selection threshold to less conservative but still reasonable values.
The pair is in fact classified as a visual double star system independently
in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).

@@

paragraph on lithium and ages

@@

% binary-single and binary-binary exchange
Another scenario that two unrelated stars may end up in a wide binary system
is multi-body gravitational scattering.
We consider the exchange probabilities in binary-single and binary-binary interactions.
Given their low binding energy compared to incoming velocity of field stars,
this is low.
Two factors that make this even more unlikely are that both stars are very young given their large Li,
and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
not HD30 with anomalous abundance patterns.
